Boundary Labeling for annotated documents

### 2017-07-24 LaTeX/Paper.tex
Paper: Added second paper to section "Previous Work". Program: No changes.

While there haven't been many papers written about this topic, they do offer interesting contributions. For example, the paper\cite{Kindermann2014} about the Luatodonotes-Package illustrates some of the different leader types available, and came to the conclusion that leaders without bends are easier to follow. %Bild einfügen?

%TODO: Über bisherige Versuche/Papers sprechen
%TODO: Was genau wollen wir erreichen?

>>>>

While there haven't been many papers written about this topic, they do offer interesting contributions. For example, the paper about the Luatodonotes-Package\cite{Kindermann2014} illustrates some of the different leader types available, and came to the conclusion that leaders without bends are easier to follow. %Bild einfügen?
However, most solutions proposed in that paper didn't care whether a leader overlapped with text or not, which resulted in a decrease in readability.

The paper by Loose\cite{Loose2015} on the other hand is based around only using the free space between the text, which produces slightly longer leaders, and forces curves. In short, the Leaders can be described as a sequence of O- and P-segments, which continue until the label's port is reached. %Überleitung zu eigenem Programm? Viele Konzepte wurden hier wiederverwendet!

%TODO: Was genau wollen wir erreichen?
